%------------------------------------------------
\textit{Doctoral Advisement}
\begin{itemize}
\item Member, Dissertation Committee: Daniel Wooten (NE), ``Predicting Fuel Salt Composition via Linear Optimization in Molten Salt
Reactors."  UC Berkeley 2019.
%
\item Chair, Dissertation Committee: Mario Ortega (NE), ``A Rayleigh Quotient Fixed Point Method for Criticality Eigenvalue Problems in Neutron Transport."  UC Berkeley 2019.
%
\item Chair, Dissertation Committee: Kelly Rowland (NE), ``Advanced Quadrature Selection for Monte Carlo Variance Reduction."  UC Berkeley 2018.
%
\item Chair, Dissertation Committee: James Bevins (NE), ``Targeted Modification of Neutron Energy Spectra for National Security Applications."  UC Berkeley 2017.
%
\item Chair, Dissertation Committee: Madicken Munk (NE), ``FW/CADIS-$\Omega$: An Angle-Informed Hybrid Method for Neutron Transport."  UC Berkeley 2017.
%
\item Chair, Dissertation Committee: Nathan Bailey (NE), ``Atom probe tomographic analysis of high dose oxide-dispersion strengthened steel (alloy MA957) at selected irradiation conditions."  UC Berkeley 2016.
%
\item co-Chair, Dissertation Committee: Sebastian Schunert (NE), ``Comparing various Spatial Discretization Schemes based on a Method of Manufactured Solution Benchmark Suite." North Carolina State University 2013.
%
\item Member, Dissertation Committee: Stephen Parker (NE), ``Synthesis, Characterization, and Neutronic Modeling of (ThxU1-x)N Fuels for Application in Compact Nuclear Reactors."  UC Berkeley 2018.
%
\item Member, Dissertation Committee: Nicholas Thompson (Nuclear Engineering and Science), ``Measuring and Validating Neutron Capture Cross Sections Using a Lead Slowing-Down Spectrometer."  Rensselaer Polytechnic Institute 2017.
%
\item Member, Dissertation Committee: Ryan Bergmann (NE), ``The Development of WARP - A Framework for Continuous Energy Monte Carlo Neutron Transport in General 3D Geometries on GPUs."  UC Berkeley 2014.
\end{itemize}

%------------------------------------------------
\textit{Master's Advisement}
\begin{itemize}
\item Chair, Thesis Committee: Marissa Ramirez Zweiger (NE), ``A Two-Grid, Nonlinear Diffusion Acceleration Method for the SN Equations with Neutron Upscattering." UC Berkeley 2018.
%
\item Chair, Thesis Committee: Mitch Negus (NE), ``Ex-Core fluence analysis of an operating rector using VERAShift." UC Berkeley 2018.
%
\item Chair, Thesis Committee: Joshua Rehak (NE), ``Weighted Delta-Tracking with Scattering implemented in the Serpent 2 Monte Carlo Code." UC Berkeley 2017.
%
\item Chair, Thesis Committee: Kelly Rowland (NE), ``Delta-tracking in the GPU-accelerated WARP Monte Carlo Neutron Transport Code." UC Berkeley 2015.
%
\item Member, Thesis Committee: Daniel Wooten (NE), ``Future needs of circulating fuel reactor kinetics modeling." UC Berkeley 2017.
%S
\item Member, Thesis Committee: Ilker Makine (NE), ``Exact Transport Representations of the Classical and Nonclassical Simplified PN Equations with Isotropic Scattering." I'lnstitut National des Sciences et Techniques 2017.
%
\item Member, Thesis Committee: Milos Atz (NE), ``Effect of initial enrichment and discharge burnup on the minimum critical mass of far-field depositions of fissile material from LWR spent fuel." UC Berkeley 2016.
%
\item Member, Thesis Committee: Dan Shen (NE), ``Preliminary feasibility assessment of molten salt cooled reactor with pin-type fuel." UC Berkeley 2016.
\end{itemize}

%------------------------------------------------
\textit{Directed Undergraduate Independent Study at UC Berkeley}
\begin{itemize}
\item Spring and Summer 2018: Alexander Blank
\item Fall 2017: Emily Vu and Jaqueline Garcia
\item Fall 2016 and Spring 2017: Eliav Maas
\end{itemize}
\textit{Directed Undergraduate Research at UC Berkeley}
\vspace*{-.6 em}
\begin{addmargin}[1em]{0 em}
Laura Shi: Jan 2019 -- present;
Emily Vu: April 2016 -- May 2019; 
Jemin Desai: Sept 2016 -- Sept 2017; 
David Smith: June 2016 -- Aug 2017; 
Mingjian Lu: June 2016 -- Aug 2017; 
Will Kable: Aug 2016 -- May 2017; 
Youdoung Zhang: Aug 2016 -- May 2017; 
Garrett Baltz: Feb 2015 -- July 2016; 
Josh Howland: Jan 2014 -- May 2016; 
Clay Sheih: Dec 2015 -- May 2016;
Soham Shah: May 2015 -- Aug 2015; 
Joseph Labrum: May 2015 -- Aug 2015; 
Marissa Ramirez-Zweiger: Nov 2014 -- Aug 2015; 
Nikola Radnovic Jan 2014 -- May2014 

\end{addmargin}

%\begin{itemize}
%\item Emily Vu: January 2018 -- May 2019
%\item David Smith: June 2016 -- Sept 2017
%\item Jemin Desai: Sept 2016 -- Sept 2017
%\item Garrett Baltz: Feb 2015 -- Aug 2015
%\item Will Kable: Aug 2016 -- Aug 2017
%\item Youdoung Zhang: Aug 2016 -- Aug 2017
%\item Josh Howland: January 2014 -- May 2016
%\end{itemize}

%------------------------------------------------
\textit{Other Scholars}
\begin{itemize}
\item Mentored Weixiong Zheng as a Postdoctoral Scholar March 2017--Dec 2018; Dr. Zheng is now employed at a Bay Area software startup 
\item Mentored Richard Vasques as an Assistant Project Scientist June 2015-- June 2017; Dr. Zheng is now a professor at The Ohio State University
\item Mentored Ilker Makine as a Visiting Scholar Summer 2017
\end{itemize}

