\begin{bibsection}
\item ``Optimal Operations of Advanced Reactors: How Do We Get There?" Current Issues in Computational Methods -- Roundtable, American Nuclear Society Annual Meeting. Online. 14 June 2021. (invited)

%\item Guest Lecture ``Nuclear Energy: Why?" for Energy 790-1
%MSE Energy Class at Georgia Tech. Online. 1 Apr.\ 2021. (invited)

\item Panelist for ``Serving the Nation: Engineering as Leaders in Government." Spring Dean's Society Event. Online 24 Mar.\ 2021. (invited)

\item ``How Can Nuclear Support a Clean Energy Future?"  American Physical Society Meeting. Online. 17 Mar.\ 2021. (invited)

\item ``Nuclear in the 2020s: considerations for the decade ahead." \textbf{Keynote Speaker}, ARPA-E Annual Fission Meeting. Online. 23 Feb.\ 2021. (invited)

%\item Guest Lecture ``Nuclear Energy: Why?" for Energy 790-1
%Emerging Energy Technologies Class at Duke University. Online. 15 Sept.\ 2020.
%(invited)

%\item Emcee for ``Good Energy Collective Meet and Great."
%Online. 11 Aug.\ 2020. 

%\item Spoke in various sessions at 2020 Nuclear Innovation
%Bootcamp. Online. 6-7 Aug.\ 2020. 

\item Panelist for ``Flexible Nuclear for Future Energy
Systems Webinar." Lucid Catalyst and ClearPath. 5 Aug.\ 2020. (invited) 

\item Panelist for `` Beyond Now: Microreactors and Near Term Demonstrations - Perspectives from
the Department of Defense and Department of Energy." Panelist. U.\ S.\ WIN Virtual
Conference. 28 July 2020. (invited) 

\item Panelist for ``Advanced Nuclear Tech in a Decarbonized Energy Future:
Feasible or Fantastical?" Duke Energy Initiative lecture series.
Online. 14 July 2020. (invited)

%\item ``How Can Nuclear Be Part of a Clean Energy Future?."
%Breakthrough Generation Bootcamp. Online. 18 June 2020. (invited)

\item Panelist for ``Challenges and Opportunities in Thermal
Hydraulics of High Temperature Gas Cooled Reactors." American Nuclear Society Annual Meeting. Online. 8 June 2020. (invited)

\item Panelist for ``Building Your Leadership Competency."
American Nuclear Society Annual Meeting. Online. 8 June 2020. (invited)

%\item ``Nuclear Engineering Research to Make a Difference." UC
%Berkeley NE Dept.\ Graduate Colloquium. Berkeley, CA. 9 March 2020.

\item ``How Can Nuclear Be Part of a Clean Energy Future?" G20
Workshop on Circular Carbon Economy. Riyadh, KSA. 5 March 2020. (invited)

\item ``Special Update: ARPA-E Nuclear Program Update." Advanced Reactors Summit VII. Knoxville, TN. 11 Feb 2020.
(invited)

%\item Moderator for ``Deploying Capital for a Clean Energy Future." BERC Energy Summit 2020. Berkeley, CA. 7 Feb 2020.
%(invited)

\item ``How Can Nuclear Energy Be Part of a Clean Energy Future?" Climate Tech Convening 2020. San Francisco, CA. 30 Jan 2020.
(invited)

\item Panelist for ``Time to be Inclusive and Pragmatic Before It’s Too Late: Advanced nuclear technologies must be a significant part of the solution set." Cleantech Forum. San Francisco, CA. 28 Jan 2020.
(invited)

\item ``The Opportunity of Next-Gen Nuclear Energy." Citizen's Climate Lobby, Fairfax Meeting. Annandale, VA. 11 Feb 2020. (invited)

\item ``What is ARPA-E Doing in Nuclear Energy?" Argonne National
Laboratory Colloquium. Lemont, IL. 20 November 2019. (invited)

%\item ``What is ARPA-E Doing in Nuclear Energy?" American
%Nuclear Society Winter Meeting MEITNER Special Session. Washington, DC. 18
%November 2019.

\item Panelist for ``The role of innovation in the civilian and
military nuclear energy sectors." The civilian-military nexus and the role of
innovation in nuclear energy, Atlantic Council. Washington, DC. 15 Oct 2019.
(invited)

%\item ``Next Generation Nuclear." Ecomodernism 2019.
%Middleburg, VA. 23 September 2019. (invited)

\item ``Nuclear and ARPA-E: Activities and Opportunities." NUC
Workshop: Innovations in Advanced Reactor Design, Analysis, and Licensing.
Raleigh, NC (given remotely). 18 September 2019. (invited)

\item ``Nuclear Energy Programs and Research at Advanced
Research Projects Agency-Energy (ARPA-E)." GABI nuclear energy roundtable.
Washington, DC. 12 September 2019. (invited)

%\item ``Optimal Operations of Advanced Reactors: If You Build
%It, Can you Run It?" ARPA-E Program Pitch. Washington, DC. 23 July 2019.

%\item ``What if Nuclear Plants Were 10x Cheaper to Operate?"
%ARPA-E Energy Summit. Denver, CO. 10 July 2019.

\item Panelist for ``Future Scientists and Engineers for Nuclear Energy." Third Symposium on US-Japan Nuclear Energy Research Cooperation. Washington, DC. 26 June 2019. (invited)

\item Panelist for ``Lessons from Solar PV." Breakthrough Dialogue 2019 Whole Earth Discipline. Sausalito, CA. 21 June 2019. (invited)

%\item ``Computing in Nuclear Engineering: Moving Beyond Today's Limitations." UW Madison Engineering Physics. Madison, WI. 28 May 2019.

%\item ``Computing in Nuclear Engineering: Moving Beyond Today's Limitations." NC State Nuclear Engineering Colloquium. Raleigh, NC. 23 May 2019.

% \item ``Computing in Nuclear Engineering: Moving Beyond Today's Limitations." GA Tech Nuclear \& Radiological Engineering Colloquium. Atlanta, GA. 10 May 2019.

\item ``Computing in Nuclear Engineering: Moving Beyond Today's Limitations." MIT Nuclear Science \& Engineering Colloquium. Cambridge, MA. 29 April 2019.

%\item ``Computing in Nuclear Engineering: Moving Beyond Today's Limitations." TAMU Nuclear Engineering Colloquium. College Station, TX. 16 April 2019.

%\item ``Creating the Future of Nuclear Energy." U Michigan Nuclear Engineering and Radiological Sciences Colloquium. Ann Arbor, MI. 18 Jan 2019. (invited)

\item ``Creating the Future of Nuclear Energy." CITRIS Research Exchange Seminar Series. Berkeley, CA. 28 Nov.\ 2018. (invited)

%\item ``Creating the Future of Nuclear Energy." Berkeley Distinguished Lectures in Data Science. Berkeley, CA. 27 Nov 2018. (invited)

%\item Panelist for ``Ethics in Nuclear Engineering and Design." American Nuclear Society. Ornaldo, FL. 13 Nov.\ 2018. (invited)

\item ``U.S.\ Nuclear Innovation System." Commercialisation of Small Nuclear in the UK. Coventry, UK. 6 Nov.\ 2018. (invited)

\item ``MEITNER: The Newest ARPA-E Program." NASA iTech. New York, NY. 14 June 2018. (invited)

\item ``Deep decarbonization: financing the rapid deployment of innovations after R\&D." 2050 Today Panel. San Fancisco, CA. 15 June 2018. (invited)

%\item ``Discussion of Future Technology Development." Nuclear R\&D Summit Panel. Washington, DC. 7 Mar.\ 2018. (invited)

%\item ``Advanced Solver for Radiation Transport." North Caroline State University Dept.\ Graduate Colloquium. Raleigh, NC. 1 Feb.\ 2018. (invited)

%\item ``Advanced Solver for Radiation Transport." Colorado School of Mines NSE Program Graduate Colloquium. Golden, CO 17 Jan.\ 2018. (invited)

\item ``Advanced Solvers for Radiation Transport." University of Illinois Urbana Champaign NPRE Dept.\ Graduate Colloquium. Champaign, IL. 5 Dec.\ 2017. (invited)

%\item Moderator for ``Commercialization of  Nuclear Fusion Summit" Moderator, Nuclear Fusion: Reacting To Commercialization by VLAB. Palo Alto, CA. 14 Nov.\ 2017. (invited)

\item ``Nuclear Energy: What Can Analytics Do for Economics and Safety?" \textbf{Keynote Speaker}, Industrial Machine Learning Workshop 17. San Francisco, CA. 24 Oct.\ 2017. (invited)

\item Panelist for ``Alternative energy, nuclear and CCS: What are the prospects?" Low-Emissions Solution Conference at the 5th International Conference on Sustainable Development. New York, NY. 21  Sept.\ 2017. (invited)

\item Panelist for ``The Case for Nuclear: Communications and Analyzing Risks and Benefits" Aspen Institute Future of Nuclear Energy Roundtable. Aspen, CO. 12  Sept.\ 2017. (invited)

\item ``Advanced Solvers and Innovation for Penetrating Radiation" \textbf{Keynote Speaker}, SPIE Penetrating Radiation Technical Event. San Diego, CA. 8 Aug.\ 2017. (invited)

%\item ``Advancing Solvers and Challenges for Nuclear Innovative." Lawrence Berkeley National Laboratory, IBT Seminar. Berkeley, CA. 12 May 2017. (invited)

\item ``Challenges \& Opportunities in Developing an Innovation Culture in Nuclear." Second Annual Third Way Advanced Nuclear Summit Panel. Washington, DC. 21 Feb.\ 2017. (invited)

\item ``Advancing Reactors with Advanced Solvers and Innovative Programs." Electric Power Research Institute. Research Meeting. Palo Alto, CA. 13 Feb.\ 2017. (invited)

\item ``Exploring the Advanced Nuclear Ecosystem." SxSW Eco Panel. Austin, TX. 12 Oct.\ 2016. (invited)

%\item ``Nuclear and Innovating the Clean Energy Landscape." French Nuclear Energy Society Young Generation Workshop. Video Meeting. 28 Sept.\ 2016. (invited)

%\item ``Nuclear and Innovating the Clean Energy Landscape." NorCal ANS Meeting. Berkeley, CA. 21 Sept.\ 2016. (invited)

%\item ``There Is So Much Room for Leadership." 2016 Nuclear Innovation Bootcamp Closing Speaker. Berkeley, CA. 12 Aug.\ 2016.\\
%\url{https://www.youtube.com/watch?v=imvnBYa9Sb0} (starting at 12 min)

%\item ``Nuclear Innovation: Concept to Execution." PHYSOR 2016. Sun Valley, ID. 2 May 2016. (invited)

%\item ``The Opportunity of Global Nuclear Innovation." UC Berkeley NE Dept.\ Graduate Colloquium. Berkeley, CA. DATE??? 2016. (invited)

\item ``The Opportunity of Global Nuclear Innovation." 49th Japan Atomic Industrial Forum (JAIF) Annual Conference. Tokyo, Japan. 12 April 2016. (invited)

\item ``Exascaling Nuclear Innovation." \textbf{Keynote speaker}, Conference on Data Analysis 2016. Santa Fe, NM. 4 Mar.\ 2016. (invited) 

%\item ``Exascaling Nuclear Innovation." BIDS Distinguished Lecture Series. 19 Feb.\ 2016. (invited) 

\item ``Let’s Get Real: When can we expect commercial
advanced reactors?." The Advanced Nuclear Summit and Showcase Panel. Washington, DC. 27 Jan.\ 2016. (invited)

\item ``Hybrid Transport Methods for Shielding Challenges." Idaho National Laboratory seminar. Idaho Falls, ID. 20 Nov.\ 2015. (invited) 

\item K.L.\ Rowland, R.N.\ Slaybaugh. ``Developments in the GPU-accelerated WARP Monte Carlo Neutron Transport Code." Workshop sur l'utilisation des acc\'{e}l\'{e}rateurs (GPUs, MICs) pour les simulations Monte-Carlo. \'{E}cole Polytechnique, Saclay, France. 10 July 2015. 

%\item R.N.\ Slaybaugh, S.C.\ Wilson. ``Solving Shielding Challenges: Self-Shielding and Strong Anisotropies." Oak Ridge National Laboratory Summer Intern Series. Oak Ridge, TN. 11 Jun.\ 2015. (invited)

%\item K.L.\ Rowland, R.M.\ Bergmann, R.N.\ Slaybaugh, J.L.\ Vujic. "Implementing delta-tracking in a GPU-accelerated Monte Carlo neutron transport code." 2nd Frontiers in Computational Physics Conference: Energy Sciences. Zurich, Switzerland. 2-5 Jun.\ 2015.  

%\item R.N.\ Slaybaugh. ``Solving Shielding Challenges: Self-Shielding and Strong Anisotropies." University of Florida NE Dept.\ Graduate Colloquium. Gainesville, FL. 2 Apr.\ 2015. (invited)

%\item R.N.\ Slaybaugh, T.M.\ Evans, and S.W.\ Mosher. ``Improved Hybrid Modeling of Used Fuel Storage Facilities." DOE-NE MPACT meeting. Oak Ridge, TN. 24-26 Mar.\ 2015. (invited)

%\item R.N.\ Slaybaugh. ``Academia Panel." WiSE O.N.E.: Theory Into Practice conference . Berkeley, CA. 14 Mar.\ 2015. (invited)

%\item ``Hybrid Methods for Shielding Challenges: Self-Shielding and Strong Anisotropies." Colorado School of Mines NSE Program Graduate Colloquium. Golden, Colorado. 7 Jan.\ 2015. (invited)

%\item ``Computational Science in the 'Real World'." Computer Science I and II, Baldwin Upper School. Bryn Mawr, PA. 10 and 11 Dec.\ 2014. (invited)

%\item ``PyNE and Nuclear Data: A Next Generation Tool." Sather Next Generation Nuclear Science Meeting. Lawrence Berkeley National Laboratory. 9 Dec.\ 2014. (invited)

%\item ``Advanced Approaches to High-Performance Computing in Nuclear: Applications to Non-Proliferation." MIIT Delegation Visit to BNRC. Berkeley, CA. 8 Dec.\ 2014. 

%\item ``Computational Methods and Software Development in Nuclear Engineering Research." Tea at Berkeley Institute for Data Science. Berkeley, CA. 4 Dec.\ 2014. (invited)

%\item ``Transitions Panel" and ``Summary Roundtable." Expanding Potential: A workshop on navigating the hurdles faced by women in STEM. Berkeley, CA. 15 Nov.\ 2014. (invited)

\item ``The PyNE Software Library: A Framework for ENSDF?" Nuclear Data Week Meeting. Brookhaven National Laboratory. 6 Nov.\ 2014. 

%\item ``The PyNE Software Library: Why and How?" ANS Northern California Local Section Meeting. Alfred's Steakhouse, San Francisco, CA. 22 Oct.\ 2014. (invited)

%\item ``What's New in Academia Panel." U.S.\ Women In Nuclear Annual Meeting. Marriott Copley Place, Boston, MA. 29 July 2014. (invited)

\item ``The Resonance Factor Method: Accelerating Monte Carlo in the Presence of Space and Energy Self-Shielding." CEA-Saclay Colloquium. Saclay, France. 26 June 2014.

%\item ``The Resonance Factor Method: Accelerating Monte Carlo in the Presence of Space and Energy Self-Shielding." Reactor Physics Methods and Analysis Group Seminar. Areva Headquarters, Paris, France. 27 June 2014.

%\item R.N.\ Slaybaugh, T.M.\ Evans, P.P.H.\ Wilson, S.C.\ Wilson. ``Radiation Transport: Computational Methods and Real-World Use.'' UC Berkeley NE Dept.\ Graduate Colloquium. Berkeley, CA. 29 Oct.\ 2012. (invited)

\item R.N.\ Slaybaugh, T.M.\ Evans, P.P.H.\ Wilson, S.C.\ Wilson. ``Radiation Transport: Computational Methods and Real-World Use.'' NC State Univ.\ NE Dept.\ Graduate Colloquium. Raleigh, NC. 8 Nov.\ 2012. (invited)

%\item ``Acceleration Methods for Massively Parallel Deterministic Transport." KAPL Employment Meeting. Niskayuna, NY. 30 Aug.\ 2011. (invited)

\item R.\ Slaybaugh, M.\ Arbidze, S. Lamichhane, D. O'Connor. ``An Evaluation of European Union Energy Policies." UW--Madison Center for World Affairs and the Global Economy Seminar. Madison, WI. 11 May 2011.

%\item ``Krylov Methods and JFNK." UW\textemdash Madison Radiation Hydrodynamics Meeting. Madison, WI. 16 Dec.\ 2010. (invited)

\item R.N.\ Slaybaugh, T.M.\ Evans, G.G.\ Davidson. ``Parallel Algorithms for Fixed-Source and Eigenvalue Problems." 2010 SIAM Annual Meeting. Pittsburgh, PA. 12-16 July 2010.

%\item ``Variance Reduction in MC21 using Forward Adjoint Variance Reduction (FAVRE)." Naval Reactors\textemdash Shielding Video-conference. Pittsburgh, PA. Aug.\ 2010.

%\item ``MC21\textemdash Jaguar Coupling for Variance Reduction." KAPL Physics Forum. Niskayuna, NY. July 2009.

\end{bibsection}


