\begin{bibsection}
\item R.N.\ Slaybaugh. ``How Can Nuclear Be Part of a Clean Energy Future?."
Breakthrough Generation Bootcamp. Online. 18 June 2020. (invited)

\item R.N.\ Slaybaugh. Panelist for ``Challenges and Opportunities in Thermal
Hydraulics of High Temperature Gas Cooled Reactors." American Nuclear Society Annual Meeting. Online. 8 June 2020. (invited)

\item R.N.\ Slaybaugh. Panelist for ``Building Your Leadership Competency."
American Nuclear Society Annual Meeting. Online. 8 June 2020. (invited)

\item R.N.\ Slaybaugh. ``Nuclear Engineering Research to Make a Difference." UC
Berkeley NE Dept.\ Graduate Colloquium. Berkeley, CA. 9 March 2020.

\item R.N.\ Slaybaugh. ``How Can Nuclear Be Part of a Clean Energy Future?" G20
Workshop on Circular Carbon Economy. Riyadh, KSA. 5 March 2020. (invited)

\item R.N.\ Slaybaugh. ``Special Update: ARPA-E Nuclear Program Update." Advanced Reactors Summit VII. Knoxville, TN. 11 Feb 2020.
(invited)

\item R.N.\ Slaybaugh. Moderator for ``Deploying Capital for a Clean Energy Future." BERC Energy Summit 2020. Berkeley, CA. 7 Feb 2020.
(invited)

\item R.N.\ Slaybaugh. ``How Can Nuclear Energy Be Part of a Clean Energy Future?" Climate Tech Convening 2020. San Francisco, CA. 30 Jan 2020.
(invited)

\item R.N.\ Slaybaugh. Panelist for ``Time to be Inclusive and Pragmatic Before It’s Too Late: Advanced nuclear technologies must be a significant part of the solution set." Cleantech Forum. San Francisco, CA. 28 Jan 2020.
(invited)

\item R.N.\ Slaybaugh. ``The Opportunity of Next-Gen Nuclear Energy." Citizen's Climate Lobby, Fairfax Meeting. Annandale, VA. 11 Feb 2020.
(invited)

\item R.N.\ Slaybaugh. ``What is ARPA-E Doing in Nuclear Energy?" Argonne National
Laboratory Colloquium. Lemont, IL. 20 November 2019. (invited)

\item R.N.\ Slaybaugh. ``What is ARPA-E Doing in Nuclear Energy?" American
Nuclear Society Winter Meeting MEITNER Special Session. Washington, DC. 18
November 2019.

\item R.N.\ Slaybaugh. Panelist for ``The role of innovation in the civilian and
military nuclear energy sectors." The civilian-military nexus and the role of
innovation in nuclear energy, Atlantic Council. Washington, DC. 15 Oct 2019.
(invited)

\item R.N.\ Slaybaugh. ``Next Generation Nuclear." Ecomodernism 2019.
Middleburg, VA. 23 September 2019. (invited)

\item R.N.\ Slaybaugh. ``Nuclear and ARPA-E: Activities and Opportunities." NUC
Workshop: Innovations in Advanced Reactor Design, Analysis, and Licensing.
Raleigh, NC (given remotely). 18 September 2019. (invited)

\item R.N.\ Slaybaugh. ``Nuclear Energy Programs and Research at Advanced
Research Projects Agency-Energy (ARPA-E)." GABI nuclear energy roundtable.
Washington, DC. 12 September 2019. (invited)

\item R.N.\ Slaybaugh. ``Optimal Operations of Advanced Reactors: If You Build
It, Can you Run It?" ARPA-E Program Pitch. Washington, DC. 23 July 2019. 

\item R.N.\ Slaybaugh. ``What if Nuclear Plants Were 10x Cheaper to Operate?"
ARPA-E Energy Summit. Denver, CO. 10 July 2019. 

\item R.N.\ Slaybaugh. Panelist for ``Future Scientists and Engineers for Nuclear Energy." Third Symposium on US-Japan Nuclear Energy Research Cooperation. Washington, DC. 26 June 2019. (invited)

\item R.N.\ Slaybaugh. Panelist for ``Lessons from Solar PV." Breakthrough Dialogue 2019 Whole Earth Discipline. Sausalito, CA. 21 June 2019. (invited)

\item R.N.\ Slaybaugh. ``Computing in Nuclear Engineering: Moving Beyond Today's Limitations." UW Madison Engineering Physics. Madison, WI. 28 May 2019.

\item R.N.\ Slaybaugh. ``Computing in Nuclear Engineering: Moving Beyond Today's Limitations." NC State Nuclear Engineering Colloquium. Raleigh, NC. 23 May 2019.

% Nuclear Workshop

\item R.N.\ Slaybaugh. ``Computing in Nuclear Engineering: Moving Beyond Today's Limitations." GA Tech Nuclear \& Radiological Engineering Colloquium. Atlanta, GA. 10 May 2019.

\item R.N.\ Slaybaugh. ``Computing in Nuclear Engineering: Moving Beyond Today's Limitations." MIT Nuclear Science \& Engineering Colloquium. Cambridge, MA. 29 April 2019.

\item R.N.\ Slaybaugh. ``Computing in Nuclear Engineering: Moving Beyond Today's Limitations." TAMU Nuclear Engineering Colloquium. College Station, TX. 16 April 2019.

\item R.N.\ Slaybaugh. ``Ask Me Anything." Cyclotron Road visit. 11 April 2019. (invited)

\item R.N.\ Slaybaugh. ``What Is ARPA-E Doing in Nuclear Energy?" Nuclear Regulatory Commission visit. 27 Mar.\ 2019. (invited)

\item R.N.\ Slaybaugh. ``What Is ARPA-E Doing in Nuclear Energy?" Office of Nuclear Energy visit. 27 Mar.\ 2019. (invited)

\item R.N.\ Slaybaugh. Panelist for ``Incorporating Innovations in Nuclear." Nuclear R\&D Summit and the Nuclear Deployment Forum. Washington, DC. 26 Mar.\ 2019. (invited)

\item R.N.\ Slaybaugh. Panelist for Agtech Innovation and Deployment ``A New Horizon for Technology in Agriculture." The Road to the Global Entrepreneurship Summit (GES) Heartland. Kansas City, MO. 19 Mar.\ 2019. (invited)

\item R.N.\ Slaybaugh. ``What Is ARPA-E Doing in Nuclear Energy?" INL Collaboration Visit. Idaho Fall, ID. 12 Feb.\ 2019. (invited)

\item R.N.\ Slaybaugh. ``What If  Advanced Reactors Could Be Autonomous?" Advanced Reactor Summit IV. San Diego, CA. 30 Jan.\ 2019. (invited)

\item R.N.\ Slaybaugh. ``Creating the Future of Nuclear Energy." U Michigan Nuclear Engineering and Radiological Sciences Colloquium. Ann Arbor, MI. 18 Jan 2019. (invited)

\item R.N..\ Slaybaugh. ``Nuclear Plant Profitability: What Will Make a Difference?" MEITNER Kickoff Meeting. Charlotte, NC. 12, Dec.\ 2018.

\item R.N.\ Slaybaugh. ``Creating the Future of Nuclear Energy." CITRIS Research Exchange Seminar Series. Berkeley, CA. 28 Nov.\ 2018. (invited)

\item R.N.\ Slaybaugh. ``Creating the Future of Nuclear Energy." Berkeley Distinguished Lectures in Data Science. Berkeley, CA. 27 Nov 2018. (invited)

\item R.N.\ Slaybaugh. Panelist for ``Ethics in Nuclear Engineering and Design."
American Nuclear Society Winter Meeting. Orlando, FL. 13 Nov.\ 2018. (invited)

\item R.N.\ Slaybaugh.  ``U.S.\ Nuclear Innovation System." Commercialisation of Small Nuclear in the UK. Coventry, UK. 6 Nov.\ 2018. (invited)

\item R.N.\ Slaybaugh. Panelist for ``A Panel Discussion on Innovation and Advanced Nuclear Power." Decarbonization and the Role of Nuclear Power. Palo Alto, CA. 6 Sept.\ 2018. (invited)
% July 20, 2019: led meeting and discussion for washington interns in science and engineering at ARPA-E HQ

\item R.N.\ Slaybaugh.  ``MEITNER: The Newest ARPA-E Program." NASA iTech. New York, NY. 14 June 2018. (invited)

\item R.N.\ Slaybaugh.  ``Deep decarbonization: financing the rapid deployment
of innovations after R\&D." 2050 Today Panel. San Francisco, CA. 15 June 2018. (invited)

\item R.N.\ Slaybaugh. ``Discussion of Future Technology Development." Nuclear R\&D Summit Panel. Washington, DC. 7 Mar.\ 2018. (invited)

\item R.N.\ Slaybaugh.  ``Advanced Solver for Radiation Transport." North Caroline State University Dept.\ Graduate Colloquium. Raleigh, NC. 1 Feb.\ 2018. (invited)

\item R.N.\ Slaybaugh.  ``Advanced Solver for Radiation Transport." Colorado School of Mines NSE Program Graduate Colloquium. Golden, CO 17 Jan.\ 2018. (invited)

\item R.N.\ Slaybaugh.  ``Advanced Solver for Radiation Transport." University of Illinois Urbana Champaign NPRE Dept.\ Graduate Colloquium. Champaign, IL. 5 Dec.\ 2017. (invited)

\item R.N.\ Slaybaugh. ``Commercialization of  Nuclear Fusion Summit" Moderator, Nuclear Fusion: Reacting To Commercialization by VLAB. Palo Alto, CA. 14 Nov.\ 2017. (invited)

\item R.N.\ Slaybaugh. ``Nuclear Energy: What Can Analytics Do for Economics and Safety?" \textbf{Keynote Speaker}, Industrial Machine Learning Workshop 17. San Francisco, CA. 24 Oct.\ 2017. (invited)

\item R.N.\ Slaybaugh. Panelist for ``Alternative energy, nuclear and CCS: What are the prospects?" Low-Emissions Solution Conference at the 5th International Conference on Sustainable Development. New York, NY. 21  Sept.\ 2017. (invited)

\item R.N.\ Slaybaugh. Panelist for ``The Case for Nuclear: Communications and Analyzing Risks and Benefits." Aspen Institute Future of Nuclear Energy Roundtable. Aspen, CO. 12  Sept.\ 2017. (invited)

\item R.N.\ Slaybaugh. ``Advanced Solvers and Innovation for Penetrating Radiation" \textbf{Keynote Speaker}, SPIE Penetrating Radiation Technical Event. San Diego, CA. 8 Aug.\ 2017. (invited)

\item R.N.\ Slaybaugh. ``Advancing Solvers and Challenges for Nuclear Innovative." Lawrence Berkeley National Laboratory, IBT Seminar. Berkeley, CA. 12 May 2017. (invited)

\item R.N.\ Slaybaugh. ``Challenges \& Opportunities in Developing an Innovation Culture in Nuclear." Second Annual Third Way Advanced Nuclear Summit Panel. Washington, DC. 21 Feb.\ 2017. (invited)

\item R.N.\ Slaybaugh. ``Advancing Reactors with Advanced Solvers and Innovative Programs." Electric Power Research Institute. Research Meeting. Palo Alto, CA. 13 Feb.\ 2017. (invited)

\item R.N.\ Slaybaugh. ``Exploring the Advanced Nuclear Ecosystem." SxSW Eco Panel. Austin, TX. 12 Oct.\ 2016. (invited)

\item R.N.\ Slaybaugh. ``Nuclear and Innovating the Clean Energy Landscape." French Nuclear Energy Society Young Generation Workshop. Video Meeting. 28 Sept.\ 2016. (invited)

\item R.N.\ Slaybaugh. ``Nuclear and Innovating the Clean Energy Landscape." NorCal ANS Meeting. Berkeley, CA. 21 Sept.\ 2016. (invited)

\item R.N.\ Slaybaugh. ``There Is So Much Room for Leadership." 2016 Nuclear Innovation Bootcamp Closing Speaker. Berkeley, CA. 12 Aug.\ 2016.\\
%\url{https://www.youtube.com/watch?v=imvnBYa9Sb0} (starting at 12 min)

\item R.N.\ Slaybaugh. ``Nuclear Innovation: Concept to Execution." PHYSOR 2016. Sun Valley, ID. 2 May 2016. (invited)

\item R.N.\ Slaybaugh. ``The Opportunity of Global Nuclear Innovation." UC Berkeley NE Dept.\ Graduate Colloquium. Berkeley, CA. DATE??? 2016. (invited)

\item R.N.\ Slaybaugh. ``The Opportunity of Global Nuclear Innovation." 49th Japan Atomic Industrial Forum (JAIF) Annual Conference. Tokyo, Japan. 12 April 2016. (invited)

\item R.N.\ Slaybaugh. ``Exascaling Nuclear Innovation." \textbf{Keynote speaker}, Conference on Data Analysis 2016. Santa Fe, NM. 4 Mar.\ 2016. (invited) 

\item R.N.\ Slaybaugh. ``Exascaling Nuclear Innovation." BIDS Distinguished Lecture Series. 19 Feb.\ 2016. (invited) 

\item R.N.\ Slaybaugh. ``Let’s Get Real: When can we expect commercial
advanced reactors?." The Advanced Nuclear Summit and Showcase Panel. Washington, DC. 27 Jan.\ 2016. (invited)

\item R.N.\ Slaybaugh. ``Hybrid Transport Methods for Shielding Challenges." Idaho National Laboratory seminar. Idaho Falls, ID. 20 Nov.\ 2015. (invited) 

\item K.L.\ Rowland, R.N.\ Slaybaugh. ``Developments in the GPU-accelerated WARP Monte Carlo Neutron Transport Code." Workshop sur l'utilisation des acc\'{e}l\'{e}rateurs (GPUs, MICs) pour les simulations Monte-Carlo. \'{E}cole Polytechnique, Saclay, France. 10 July 2015. 

\item R.N.\ Slaybaugh, S.C.\ Wilson. ``Solving Shielding Challenges: Self-Shielding and Strong Anisotropies." Oak Ridge National Laboratory Summer Intern Series. Oak Ridge, TN. 11 Jun.\ 2015. (invited)

\item K.L.\ Rowland, R.M.\ Bergmann, R.N.\ Slaybaugh, J.L.\ Vujic. "Implementing delta-tracking in a GPU-accelerated Monte Carlo neutron transport code." 2nd Frontiers in Computational Physics Conference: Energy Sciences. Zurich, Switzerland. 2-5 Jun.\ 2015.  

\item R.N.\ Slaybaugh. ``Solving Shielding Challenges: Self-Shielding and Strong Anisotropies." University of Florida NE Dept.\ Graduate Colloquium. Gainesville, FL. 2 Apr.\ 2015. (invited)

\item R.N.\ Slaybaugh, T.M.\ Evans, and S.W.\ Mosher. ``Improved Hybrid Modeling of Used Fuel Storage Facilities." DOE-NE MPACT meeting. Oak Ridge, TN. 24-26 Mar.\ 2015. (invited)

\item R.N.\ Slaybaugh. ``Academia Panel." WiSE O.N.E.: Theory Into Practice conference . Berkeley, CA. 14 Mar.\ 2015. (invited)

\item R.N.\ Slaybaugh. ``Hybrid Methods for Shielding Challenges: Self-Shielding and Strong Anisotropies." Colorado School of Mines NSE Program Graduate Colloquium. Golden, Colorado. 7 Jan.\ 2015. (invited)

\item Rachel Slaybaugh. ``Computational Science in the 'Real World'." Computer Science I and II, Baldwin Upper School. Bryn Mawr, PA. 10 and 11 Dec.\ 2014. (invited)

\item R.N.\ Slaybaugh. ``PyNE and Nuclear Data: A Next Generation Tool." Sather Next Generation Nuclear Science Meeting. Lawrence Berkeley National Laboratory. 9 Dec.\ 2014. (invited)

\item R.N.\ Slaybaugh. ``Advanced Approaches to High-Performance Computing in Nuclear: Applications to Non-Proliferation." MIIT Delegation Visit to BNRC. Berkeley, CA. 8 Dec.\ 2014. 

\item R.N.\ Slaybaugh. ``Computational Methods and Software Development in Nuclear Engineering Research." Tea at Berkeley Institute for Data Science. Berkeley, CA. 4 Dec.\ 2014. (invited)

\item R.N.\ Slaybaugh. ``Transitions Panel" and ``Summary Roundtable." Expanding Potential: A workshop on navigating the hurdles faced by women in STEM. Berkeley, CA. 15 Nov.\ 2014. (invited)

\item R.N.\ Slaybaugh. ``The PyNE Software Library: A Framework for ENSDF?" Nuclear Data Week Meeting. Brookhaven National Laboratory. 6 Nov.\ 2014. 

\item R.N.\ Slaybaugh. ``The PyNE Software Library: Why and How?" ANS Northern California Local Section Meeting. Alfred's Steakhouse, San Francisco, CA. 22 Oct.\ 2014. (invited)

\item R.N.\ Slaybaugh. ``What's New in Academia Panel." U.S.\ Women In Nuclear Annual Meeting. Marriott Copley Place, Boston, MA. 29 July 2014. (invited)

\item R.N.\ Slaybaugh. ``The Resonance Factor Method: Accelerating Monte Carlo in the Presence of Space and Energy Self-Shielding." CEA-Saclay Colloquium. Saclay, France. 26 June 2014.

\item R.N.\ Slaybaugh. ``The Resonance Factor Method: Accelerating Monte Carlo in the Presence of Space and Energy Self-Shielding." Reactor Physics Methods and Analysis Group Seminar. Areva Headquarters, Paris, France. 27 June 2014.

\item R.N.\ Slaybaugh, T.M.\ Evans, P.P.H.\ Wilson, S.C.\ Wilson. ``Radiation Transport: Computational Methods and Real-World Use.'' UC Berkeley NE Dept.\ Graduate Colloquium. Berkeley, CA. 29 Oct.\ 2012. (invited)

\item R.N.\ Slaybaugh, T.M.\ Evans, P.P.H.\ Wilson, S.C.\ Wilson. ``Radiation Transport: Computational Methods and Real-World Use.'' NC State Univ.\ NE Dept.\ Graduate Colloquium. Raleigh, NC. 8 Nov.\ 2012. (invited)

\item R.N.\ Slaybaugh. ``Acceleration Methods for Massively Parallel Deterministic Transport." KAPL Employment Meeting. Niskayuna, NY. 30 Aug.\ 2011. (invited)

\item R.\ Slaybaugh, M.\ Arbidze, S. Lamichhane, D. O'Connor. ``An Evaluation of European Union Energy Policies." UW--Madison Center for World Affairs and the Global Economy Seminar. Madison, WI. 11 May 2011.

\item R.N.\ Slaybaugh. ``Krylov Methods and JFNK." UW\textemdash Madison Radiation Hydrodynamics Meeting. Madison, WI. 16 Dec.\ 2010. (invited)

\item R.N.\ Slaybaugh, T.M.\ Evans, G.G.\ Davidson. ``Parallel Algorithms for Fixed-Source and Eigenvalue Problems." 2010 SIAM Annual Meeting. Pittsburgh, PA. 12-16 July 2010.

\item R.N.\ Slaybaugh. ``Variance Reduction in MC21 using Forward Adjoint Variance Reduction (FAVRE)." Naval Reactors\textemdash Shielding Video-conference. Pittsburgh, PA. Aug.\ 2010.

\item R.N.\ Slaybaugh. ``MC21\textemdash Jaguar Coupling for Variance Reduction." KAPL Physics Forum. Niskayuna, NY. July 2009.

\end{bibsection}


