\begin{bibsection}
\item Suzanne Baker, Jessica Lovering, \textbf{Rachel Slaybaugh}, and Denia Djokic. ``A Policy Pathway for Nuclear Justice." Policy Report for Good Energy Collective. April 27, 2021. %\url{https://www.goodenergycollective.org/policy/a-policy-pathway-for-nuclear-justice}

\item R.\ Martineau, D.\ Andrs, R.\ Carlsen, D.\ Gaston, J.\ Hansel, F.\ Kong, A.\ Lindsay, C.\ Permann, A.\ Slaughter, E.\ Merzari, R.\ Hu, \textit{A.\ Novak}, \textbf{R.\ Slaybaugh}. ``Multiphysics for
Nuclear Energy Applications Using a Cohesive Computational Framework."
\textit{Nuclear Engineering and Design}. \textbf{367} (2020) 1107512.%\\
%\url{https://doi.org/10.1016/j.nucengdes.2020.110751}\\

\item \textbf{Rachel Slaybaugh}, Joel Fetter, Curt Nehrkorn, Geoffrey Short. ``Generating Electricity Managed by Intelligent Nuclear
Assets (GEMINA)." Funding Opportunity No.\ DE-FOA-002174. (Oct 2019)%\\
%\url{https://arpa-e-foa.energy.gov/#FoaId4f8d5ac3-267d-4849-ad63-80f858761a74}

\item \textit{Madicken Munk}, \textbf{Rachel Slaybaugh}, ``Review of Hybrid Methods for Deep-Penetration Neutron Transport."  \textit{Nuclear Science and Engineering}. \textbf{193}:10 (2019) 1055-1089.%\\
%\url{https://www.tandfonline.com/doi/full/10.1080/00295639.2019.1586273}

\item \textit{James E.\ Bevins}, \textbf{R.N.\ Slaybaugh}. ``Gnowee: A Metaheuristic Optimization Algorithm for Solving Engineering Problems Containing Continuous and Discrete Design Parameters." \textit{Nuclear Technology}. \textbf{205}:4 (2019) 542-562.%\\
%\url{http://arxiv.org/abs/1804.05429}

\item \textbf{R.N.\ Slaybaugh}, \textit{M.\ Ramirez-Zweiger}, Tara Pandya, Steven Hamilton, T.M.\ Evans. ``Eigenvalue Solvers for Modeling Nuclear Reactors on Leadership Class Machines," \textit{Nuclear Science and Engineering}. \textbf{190} (2017) 31-44.%\\
%\url{https://arxiv.org/abs/1708.04928}

\item Jeffery B.\ Greenblatt, Nicholas R. Brown, \textbf{Rachel Slaybaugh}, Theresa Wilks, Emma Stewart, and Sean T. McCoy. ``The Future of Low-Carbon Electricity,'' \textit{Annual Review of Environment and Resources}. \textbf{42} (2017) 289-316. %\\
%\url{http://www.annualreviews.org/doi/10.1146/annurev-environ-102016-061138}
\end{bibsection}

